%% Fall 2013 MDM Homework One
\documentclass[12pt,letterpaper]{article}

\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage[left=2cm,right=2cm,top=2cm,bottom=2cm,headheight=22pt]{geometry}
\usepackage{fancyhdr}
\usepackage{setspace}
\usepackage{lastpage}
\usepackage{url}

\theoremstyle{definition}
\newtheorem{task}{Task}

\begin{document}

%other parameters
\setlength{\parskip}{1ex plus 0.5ex minus 0.2ex}
\setlength{\parindent}{0pt}

%header and footer parameters
\pagestyle{fancy}
\lhead{Math 1100}
\chead{Weekly Homework}
\rhead{Due: Friday, January 15}
\lfoot{} 
\cfoot{\emph{Prof. Hitchman}} 
\rfoot{} 

\begin{center}
{
\Large
\textbf{Graphs: Assignment \#1}
}
\end{center}

Your paper should have the following information on it.
\begin{itemize}
\item Your name
\item Your student ID number 
\item Which section you are in: 02 MWF, or 04 TTh
\end{itemize}


\subsection*{Specifications for Grading}

To earn a passing mark, your assignment must:
\begin{itemize}
\item be typed, and at least one page and no more than two pages in length. Diagrams may be hand drawn.
\item address the tasks and questions below.
\item explain your ideas in complete sentences. Use paragraphs to organize your thoughts.
\item conform to reasonable standards for grammar, spelling, and usage of the English language with minimal errors. (You may consider seeking help on writing from the Writing Center in the Academic Learning Center. http://www.uni.edu/unialc/writing-center)
\item be turned in by 3pm on Friday, January 22.
\end{itemize}



\subsection*{What to do}

\begin{task}
Go to the web site \url{http://planarity.net/} and play the game for a while. Report what level you reached. 
Was this game any fun? Do you feel like you understand the idea of ``planarity'' any better?
\end{task}

\begin{task}
Draw an example of a connected graph that has degree sequence $\{4,4,2,2,2 \}$. Label the vertices with their degrees to check your work.

Is it possible to draw a graph with degree sequence $\{4,4,3,2,2\}$? If so, draw it. If not, explain what the problem is.
\end{task}

\begin{task}
Draw an example of a graph with five vertices, call them $A, B, C, D, E$, which has a cycle of length 3 and a cycle of length 4.

Does your graph have a cycle of length 5? Is it possible to make such a graph without a cycle of length 5? Explain your reasoning.
\end{task}

\end{document}


















